On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-06-28 Manuscript/manuscript.tex
more small changes to end of Data section

\begin{figure}[tbp]
  \centering
  \includegraphics{Scatterplot2019vs2022}
  \caption{The reaction times from athletes who competed at least once in both 
  the 2019 and 2022 World Track and Field Championships}
  \label{Scatterplot2019vs2022}
\end{figure}
\of{I included this here for now, but feel free to change the location.  I will
add references to it and explanation of it along with some descriptive statistics about
the size and mean/median,std dev, size of the data.}
\jy{Show dot plots which would give the distribution; without uncertainty
  measure, the mean does not tell much.}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics{Scatterplot2019vs2022}
  \caption{The reaction times from athletes who competed at least once in both 
  the 2019 and 2022 World Track and Field Championships}
  \label{fig:Scatterplot2019vs2022}
\end{figure}
\of{I included this here for now, but feel free to change the location.  I will
add references to it and explanation of it along with some descriptive statistics about
the size and mean/median,std dev, size of the data.}
\jy{Show dot plots which would give the distribution; without uncertainty
  measure, the mean does not tell much.}

Figure~\ref{fig:Scatterplot2019vs2022} shows the distribution of times from the
2019 and 2022 World Championships.  This data was only for athletes who competed
in at least one race at each championship, however it is possible for athletes
to have competed in one race in 2019 and two races in 2022.  The 2022 World
Championship Heats and Semifinals both had on average lower reaction times than
their respective 2019 races, and the 2022 finals were substantially faster.  Also
worth noting is that the fastest reaction time in the 2022 Finals and 2022
Semifinals both came from Devon Allen, but the difference between 0.101 and 0.009
seconds was the difference in what caused him to be disqualified.
